<!--
%\VignetteEngine{knitr::docco_linear}
%\VignetteIndexEntry{The archivist package compendium}
-->

# Archiving artifacts with their chaining code

The **archivist** package is very efficient and advantageous when the archived artifacts were created with a chaining code, offered by [dplyr](https://github.com/hadley/dplyr) package. It is higly useful because the origin of the artifact is archived, what means that the artifact can be easly reproduced and it's origin code is stored for future use.

Below are examples of creating artifacts with a chaining code, that requires using a `%>%` and  a `%.%` operators, offered by **dplyr** package.

Let us prepare a [**Repository**](https://github.com/pbiecek/archivist/wiki/archivist-package-Repository) where archived artifacts will be stored.
```{r, message=FALSE,comment="", warning=FALSE}
library(devtools)
install_github("archivist", "pbiecek")
library(archivist)
exampleRepoDir <- getwd()
createEmptyRepo( exampleRepoDir )
```

Then one might create artifacts like those below. The code lines are ordered in chaining code, which will be used by `saveToRepo` function to store an artifact and archive it's origin code as a `name` of this artifact.
```{r, message=FALSE,comment="", warning=FALSE}
# example 1
library(dplyr)

data("hflights", package = "hflights")
hflights %>%
   group_by(Year, Month, DayofMonth) %>%
   select(Year:DayofMonth, ArrDelay, DepDelay) %>%
   summarise(
      arr = mean(ArrDelay, na.rm = TRUE),
      dep = mean(DepDelay, na.rm = TRUE)
   ) %>%
   filter(arr > 30 | dep > 30) %>%
   saveToRepo( exampleRepoDir )  
```

One may see a vast difference in code evalution when using chaining code.
Here is an example of traditional `R` call and one that uses `chaining code` philosophy.
```{r, message=FALSE,comment="", warning=FALSE}
# example 2
library(Lahman)

# Traditional R code
players <- group_by(Batting, playerID)
games <- summarise(players, total = sum(G))
head(arrange(games, desc(total)), 5)

# Corresponding chaining code
Batting %.%
   group_by(playerID) %.%
   summarise(total = sum(G)) %.%
   arrange(desc(total)) %.%
   head(5) %>%
   saveToRepo( exampleRepoDir )
```

Many of various operations can be performed on a single `data.frame` before one consideres to archive this artifacts. The **archivist** guarantees that all of them will be `archived`, which means a code alone will no longer be needed to be stored in a separate file. The `CrimeStatebyState` data set can be downloaded from [here](https://github.com/MarcinKosinski/Museum).
```{r, message=FALSE,comment="", warning=FALSE}
# example 3
crime.by.state <- read.csv("CrimeStatebyState.csv")
crime.by.state %.%
   filter(State=="New York", Year==2005) %.%
   arrange(desc(Count)) %.%
   select(Type.of.Crime, Count) %.%
   mutate(Proportion=Count/sum(Count)) %.%
   group_by(Type.of.Crime) %.%
   summarise(num.types = n(), counts = sum(Count)) %>%
   saveToRepo( exampleRepoDir )
```

Dozens of artifacts may now be stored in one, full of links **Repository**.
```{r, message=FALSE,comment="", warning=FALSE}
# example 4
library(ggplot2)

diamonds %.% 
   group_by(cut, clarity, color) %.%  
   summarize(
      meancarat = mean(carat, na.rm = TRUE), 
      ndiamonds = length(carat)
   ) %>%
head( 10) %>%
   saveToRepo( exampleRepoDir )
```

One might save artifact's [`md5hash`](https://github.com/pbiecek/archivist/wiki/archivist-package-md5hash) in case to check his origin stored in a [`Tag`](https://github.com/pbiecek/archivist/wiki/archivist-package---Tags)
named `name`.
```{r, message=FALSE,comment="", warning=FALSE}
# example 5
data(mtcars)
hash <- mtcars %.% 
   group_by(cyl, am) %.%
   select(mpg, cyl, wt, am) %.%
   summarise(avgmpg = mean(mpg), avgwt = mean(wt)) %.%
   filter(avgmpg > 20) %>%
   saveToRepo( exampleRepoDir )

```

After archiving all desired artifacts created with their chaining code, the summary of the **Repository** might be performed. Below is a single call of stored artifacts' names and the summary of the whole created **Repository** in this use case.

```{r, message=FALSE,comment="", warning=FALSE}
# summary
showLocalRepo( exampleRepoDir )[, 2]
summaryLocalRepo( exampleRepoDir )

```

One can restore the origin of artifact created in example 5.
```{r, message=FALSE,comment="", warning=FALSE}
returnTag( md5hash = hash, exampleRepoDir )
```

```{r, echo=FALSE, results='hide'}
deleteRepo( exampleRepoDir )
```



