---
layout:  page
title: "Chaining"
comments:  true
published:  true
categories: [Use Case]
output:
  html_document:
    mathjax:  default
    fig_caption:  true
---
```{r, echo=FALSE}
library(knitr)
opts_chunk$set(comment="", message=FALSE, warning = FALSE,
							 tidy.opts=list(keep.blank.line=TRUE,
							 							 width.cutoff=150),
							 options(width=150))
```

The **archivist** package is very efficient and advantageous when archived artifacts were created with a chaining code offered by the [magrittr](http://cran.r-project.org/web/packages/magrittr/index.html) package. It is higly useful because the origin of the artifact is archived, which means that the artifact can be easly reproduced and it's origin code is stored for future use. 

Below are examples of creating artifacts with a chaining code, that requires using a `%>%` and  a `%.%` operators, offered by the **magrittr** and the **dplyr** package.

Since the version 1.5 of the **magrittr** package has changed functionality of a mentioned pipe operator `%>%`, we copied (in version 1.3 of the **archivist**) functionality from version 1.0.1 and added old operator to the **archivist** package as `%a%` operator.



Let us prepare a [**Repository**](https://github.com/pbiecek/archivist/wiki/archivist-package-Repository) where archived artifacts will be stored.
```{r}
library(archivist)
exampleRepoDir <- getwd()
createLocalRepo(exampleRepoDir, default = TRUE)
```

# Chaining code

Then one might create artifacts like those below. The code lines are ordered in chaining code, which will be used by the `asave` function to store an artifact and archive it's origin code as a `name` of this artifact.
```{r}
# example 1
library(dplyr)

data("hflights", package = "hflights")
hflights %a%
   group_by(Year, Month, DayofMonth) %a%
   select(Year:DayofMonth, ArrDelay, DepDelay) %a%
   summarise(
      arr = mean(ArrDelay, na.rm = TRUE),
      dep = mean(DepDelay, na.rm = TRUE)
   ) %a%
   filter(arr > 30 | dep > 30) -> example1
```

One may see a vast difference in code evalution when using chaining code.
Here is an example of a traditional `R` call and one that uses the `chaining code` philosophy.
```{r}
# example 2
library(Lahman)

# Traditional R code
players <- group_by(Batting, playerID)
games <- summarise(players, total = sum(G))
head(arrange(games, desc(total)), 5)

# Corresponding chaining code
Batting %a%
   group_by(playerID) %a%
   summarise(total = sum(G)) %a%
   arrange(desc(total)) %a%
   head(5) %a%
   asave( repoDir = exampleRepoDir )
```

# `setLocalRepo`

To simplify the code one can set globally the path to **Repository** using code as below. Now one no longer need to specify the `repoDir` parameter with every call.
```{r}
setLocalRepo( exampleRepoDir )
```

# Archiving artifacts


Many of various operations can be performed on a single `data.frame` before one consideres to archive these artifacts. **Archivist** guarantees that all of them will be `archived`, which means a code alone will no longer be needed to be stored in a separate file. Also an artifact may be saved during operations are performed and used in further code evaluations. This can be done when
argument \code{value = TRUE} in `asave` is specified.
```{r}
# example 3
aread('MarcinKosinski/Museum/3374db20ecaf2fa0d070d') -> crime.by.state
crime.by.state %a%
   filter(State=="New York", Year==2005) %a%
   arrange(desc(Count)) %a%
   select(Type.of.Crime, Count) %a%
   mutate(Proportion=Count/sum(Count)) %a%
   asave( exampleRepoDir, value = TRUE) %a%
   group_by(Type.of.Crime) %a%
   summarise(num.types = n(), counts = sum(Count)) %a%
   asave( )
```


Dozens of artifacts may now be stored in one **Repository**. Every artifact
may have an additional Tag specified by an user. This will simplify searching for this artifact in the future.
```{r}
# example 4
library(ggplot2)

diamonds %a% 
   group_by(cut, clarity, color) %a%  
   summarize(
      meancarat = mean(carat, na.rm = TRUE), 
      ndiamonds = length(carat)
   ) %a% 
   head( 10) %a%
   asave(userTags = c("tags", "operations on diamonds"))
```

# Restoring origin code - Artifact's Pedigree

```{r, results = 'asis'}
# results = 'asis'
hash2 <- searchInLocalRepo( pattern = "operations on diamonds" )
ahistory(hash2, format = "kable")
```



