---
title: "archivist: An R Package for Managing, Recording and Restoring Data Analysis Results"
author: "Replication script"
output: html_document
---

# Intro

This is the replication script for 'archivist: An R Package for Managing, Recording and Restoring Data Analysis Results' (Przemyslaw Biecek, Marcin Kosinski) submitted to JSS. 

First, make sure that `archivist` is installed.

```{r}
if (!require(archivist)) {
  install.packages("archivist")
  library(archivist)
}
```

# Section 2.1

Creation of hooks to R objects.
Following lines download R objects from remote repository.

```{r}
archivist::aread("pbiecek/graphGallery/2166dfbd3a7a68a91a2f8e6df1a44111")
```

These instructions retrieve R objects from graphGallery directory attached to the archivist package.

```{r}
setLocalRepo(system.file("graphGallery", package = "archivist"))
# plot
archivist::aread("2166dfbd3a7a68a91a2f8e6df1a44111")
archivist::aread("2166d")

# regression model
model <- archivist::aread("2a6e492cb6982f230e48cf46023e2e4f")
summary(model)
```



# Section 2.2

Retrieval of a list of R objects with given tags.

Following lines search within remote repositories and download objects with given properties.

```{r}
models <- asearch("pbiecek/graphGallery", patterns = c("class:lm", "coefname:Sepal.Length"))

lapply(models, coef)
```

And from the local repository.

```{r}
models <- asearch(patterns = c("class:lm", "coefname:Sepal.Length"))

lapply(models, coef)
```

```{r}
## from global
#plots <- asearch("pbiecek/graphGallery", 
#    patterns = c("class:gg", "labelx:Sepal.Length"))

# from local
plots <- asearch(patterns = c("class:gg", "labelx:Sepal.Length"))
length(plots)

library("gridExtra")
do.call(grid.arrange,  plots)
```

# Section 2.3

Retrieval of the object's pedigree.


```{r, message=FALSE, warning=FALSE}
library("archivist")
library("dplyr")
createEmptyRepo("tmp_archivist", default = TRUE)

data(iris)

iris %a%
   filter(Sepal.Length < 6) %a%
   lm(Petal.Length~Species, data=.) %a%
   summary() -> tmp

ahistory(tmp)

ahistory(md5hash = "050e41ec3bc40b3004bc6bdd356acae7")
```

# Section 3.1

Repository management.

Creation of a new empty repository.

```{r}
# global path
repo <- "/Users/pbiecek/GitHub/new_repo"
# local path
repo <- "new_repo"
createEmptyRepo(repoDir = repo, default = TRUE)
```

Deletion of an existing repository


```{r}
repo <- "new_repo"
deleteRepo(repoDir = repo)
```


Copying artifacts from other repositories.

```{r}
repo <- "new_repo"
createEmptyRepo(repoDir = repo)
copyGithubRepo(repoTo = repo, md5hashes= "2166dfbd3a7a68a91a2f8e6df1a44111", 
         user = "pbiecek", repo = "graphGallery")
```

Showing repository statistics


```{r}
showLocalRepo(repoDir = repo, method = "tags")
```

```{r}
summaryLocalRepo(repoDir = 
    system.file("graphGallery", package = "archivist")) 
```

Setting default repository

```{r}
setGithubRepo(user = "pbiecek", repo = "graphGallery")
setLocalRepo(repoDir = system.file("graphGallery", package = "archivist"))
```

Saving to the default repository.

```{r}
setLocalRepo(repoDir = repo)
saveToRepo(iris)
```


# Section 3.2

Artifact management

Saving an R object into a repository

```{r}
library("ggplot2")
repo <- "new_repo"
pl <- qplot(Sepal.Length, Petal.Length, data = iris)
saveToRepo(pl, repoDir = repo)

showLocalRepo(repoDir = repo, "tags")

# deleteRepo(repo)
```


Serialization of an object creation event into repository

```{r}
library("dplyr")
iris %a%
   filter(Sepal.Length < 6) %a%
   lm(Petal.Length~Species, data=.) %a%
   summary() -> tmp

ahistory(tmp)
ahistory(md5hash = "050e41ec3bc40b3004bc6bdd356acae7")
```

Loading an object from repository, remote, local or in a package.

```{r}
pl2 <- loadFromGithubRepo("92ada1e052d4d963e5787bfc9c4b506c", repo="graphGallery", user="pbiecek", 
                             value=TRUE)
pl3 <- loadFromLocalRepo("92ada1", system.file("graphGallery", package = "archivist"), value=TRUE)

archivist::aread("pbiecek/graphGallery/2166dfbd3a7a68a91a2f8e6df1a44111")

setLocalRepo(system.file("graphGallery", package = "archivist"))

pl3 <- loadFromLocalRepo("92ada1", value=TRUE)

archivist::aread("2166d")
```

```{r}
setLocalRepo(system.file("graphGallery", package = "archivist"))
model <- aread("2a6e492cb6982f230e48cf46023e2e4f")
digest::digest(model)
```

Removal of an object from repository

```{r}
rmFromRepo("92ada1e052d4d963e5787bfc9c4b506c", repoDir = repo)
```

Remove all older than 30 days

```{r}
obj2rm <- searchInLocalRepo(list(dateFrom = "2010-01-01", dateTo = Sys.Date()-30), repoDir = repo)

rmFromRepo(obj2rm, repoDir = repo, many = TRUE)
```


Search for an artifact
Search in a local/GitHub repository

```{r}
searchInLocalRepo(pattern = "class:gg", 
    repoDir = system.file("graphGallery", package = "archivist"))

searchInLocalRepo(pattern = list(dateFrom = "2014-09-01",
    dateTo = "2014-09-30" ), 
    repoDir = system.file("graphGallery", package = "archivist"))


multiSearchInLocalRepo(pattern=c("class:gg", "labelx:Sepal.Length"),
         repoDir = system.file("graphGallery", package = "archivist"))	
```

Interactive search

```{r, eval=FALSE}
arepo <- system.file("graphGallery", package = "archivist")
shinySearchInLocalRepo(arepo)
```

Delete

```{r}
deleteRepo("new_repo")
```


# R Session

```{r}
sessionInfo()
```


